---
title: "Ejemplo de incorporación de datos a la base de datos: parcelas LaPaz,
Matitas, Plato"
author: "Marius Bottin"
lang: es
format: 
  gfm:
    df-print: kable
knitr: 
  opts_chunk: 
    fig.path: "./Fig/Incor_3parcelas"
---

```{r}
DIR_DATA <- "../../otherData/"
dir(DIR_DATA)
encod<-stringi::stri_enc_detect(paste0(DIR_DATA,"/LaPaz.csv"))[[1]]$Encoding[1]
plots<-c("LaPaz","Matitas","Plato")
parcelas<-lapply(paste(DIR_DATA,paste(plots,"csv",sep="."),sep="/"),read.csv,dec=",",sep=";", fileEncoding=encod)
names(parcelas) <- plots
# corrección puntual: hay un "1" en las latitudes de LaPaz que no tiene sentido
parcelas$LaPaz$latitude_decimal[parcelas$LaPaz$latitude_decimal==1]<-NA
parcelas_tot <- data.frame(id=1:sum(sapply(parcelas,nrow)),plot=rep(names(parcelas),sapply(parcelas,nrow)),Reduce(rbind, parcelas))
```

## Correction of tags that blocks the individual unicities


```{r}
parcelas_tot$ind[parcelas_tot$plot=="LaPaz"&parcelas_tot$individualID=="394A"]<-"494"
parcelas_tot$individualID[parcelas_tot$plot=="LaPaz"&parcelas_tot$individualID=="394A"]<-"494A"

parcelas_tot$ind[parcelas_tot$plot=="Plato"&parcelas_tot$individualID=="514B"]<-"541"
parcelas_tot$individualID[parcelas_tot$plot=="Plato"&parcelas_tot$individualID=="514B"]<-"541B"

parcelas_tot$ind[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1275A"]<-"1235"
parcelas_tot$individualID[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1275A"]<-"1235A"

parcelas_tot$ind[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1410B"]<-"2410"
parcelas_tot$individualID[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1410B"]<-"2410B"

parcelas_tot$ind[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1425A"&parcelas_tot$subplot==64]<-"2425"
parcelas_tot$individualID[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1425A"&parcelas_tot$subplot==64]<-"2425A"
parcelas_tot$ind[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1430A"&parcelas_tot$subplot==64]<-"2430"
parcelas_tot$individualID[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1430A"&parcelas_tot$subplot==64]<-"2430A"
parcelas_tot$ind[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1435A"&parcelas_tot$subplot==64]<-"2435"
parcelas_tot$individualID[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1435A"&parcelas_tot$subplot==64]<-"2435A"

parcelas_tot$ind[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1737D"]<-"1437"
parcelas_tot$individualID[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="1737D"]<-"1437D"


parcelas_tot$ind[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="2552A"]<-"2452"
parcelas_tot$individualID[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="2552A"]<-"2452A"


parcelas_tot$ind[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="2575A"]<-"2675"
parcelas_tot$individualID[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="2575A"]<-"2675A"

parcelas_tot$ind[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="3279A"]<-"2379"
parcelas_tot$individualID[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="3279A"]<-"2379A"

parcelas_tot$ind[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="3342"&parcelas_tot$subplot==88]<-"3442"
parcelas_tot$individualID[parcelas_tot$plot=="Matitas"&parcelas_tot$individualID=="3342"&parcelas_tot$subplot==88]<-"3442"
```

## Connect to the database

```{r}
pp_bst <- RPostgres::dbConnect(RPostgres::Postgres(), dbname = "pp_bst_col")
```

## Methodology and variables

```{r}
def_unit <- RPostgres::dbReadTable(pp_bst, DBI::Id(schema = "main", table="def_unit"))
stopifnot("Number of individuals" %in% def_unit$unit)
def_var <- RPostgres::dbReadTable(pp_bst, DBI::Id(schema = "main", table="def_var"))
stopifnot("qt_int" %in% def_var$name_var)
def_method <- RPostgres::dbReadTable(pp_bst, DBI::Id(schema = "main", table="def_method"))
stopifnot("Permanent plot 1 (to be defined)" %in% def_method$method)
```

## Spatial data

### Sending individual coordinates

```{r}
library(spData)
library(sf)
CRS<-3116
CRS_orig<-4326
worldData<-spData::world
colombia<-st_geometry(worldData[worldData$name_long=="Colombia",]) %>% st_set_crs(CRS_orig) %>% st_transform(CRS)
sf_parcelas<-st_as_sf(parcelas_tot[!is.na(parcelas_tot$longitude_decimal) & !is.na(parcelas_tot$latitude_decimal), ], coords=c("longitude_decimal","latitude_decimal")) %>% st_set_crs(CRS_orig) %>% st_transform(CRS)
st_write(obj = sf_parcelas, dsn = pp_bst, layer = DBI::Id(schema = "tmp", table = "parcelas"), delete_layer = T)
```
### Building the plot polygons

En este caso particular tenemos que construir los objetos espaciales que
se van a referenciar.

```{r}
RPostgres::dbGetQuery(pp_bst,"
WITH a AS(
    SELECT plot,min(ST_X(geometry)) min_x,min(ST_Y(geometry)) min_y,max(ST_X(geometry)) max_x,max(ST_Y(geometry)) max_y
    FROM tmp.parcelas
    GROUP BY plot 
)
SELECT plot,
  ST_Distance(ST_SetSrid(ST_MakePoint(min_x,min_y),3116), ST_SetSrid(ST_MakePoint(min_x,max_y),3116)) distSN,
  ST_Distance(ST_SetSrid(ST_MakePoint(min_x,min_y),3116), ST_SetSrid(ST_MakePoint(max_x,min_y),3116)) distWE
FROM a
;")
```

```{r}
# CREATE A TABLE WITH TEMPORARY OBJECTS FOR THE PROJECTS POLYGONS
if(RPostgres::dbExistsTable(pp_bst,DBI::Id(schema="tmp",table="spatproject")))
{RPostgres::dbExecute(pp_bst,"DROP TABLE tmp.spatproject")}
```

```{r}
RPostgres::dbExecute(pp_bst,"
CREATE TABLE tmp.spatproject AS(
WITH a AS(
    SELECT plot,min(ST_X(geometry)) min_x,min(ST_Y(geometry)) min_y,max(ST_X(geometry)) max_x,max(ST_Y(geometry)) max_y
    FROM tmp.parcelas
    GROUP BY plot 
)
SELECT 
  plot,
  ST_SetSRID(ST_makePolygon(ST_MakeLine(ARRAY[st_makepoint(min_x,min_y),ST_MakePoint(min_x,max_y), ST_MakePoint(max_x,max_y), ST_MakePoint(max_x,min_y), ST_MakePoint(min_x,min_y)])),3116) geom
FROM a
)")
```

### Building the subplot spatial objects

#### Defining the grid function in PL/PSQL

Creating the function to create grids as polygons (which we will use as
subplots)

<https://gis.stackexchange.com/questions/16374/creating-regular-polygon-grid-in-postgis>

```{r}
RPostgres::dbExecute(pp_bst,"
CREATE OR REPLACE FUNCTION public.makegrid_2d (
  bound_polygon public.geometry,
  grid_step integer,
  metric_srid integer = 28408 --metric SRID (this particular is optimal for the Western Russia)
)
RETURNS public.geometry AS
$body$
DECLARE
  BoundM public.geometry; --Bound polygon transformed to the metric projection (with metric_srid SRID)
  Xmin DOUBLE PRECISION;
  Xmax DOUBLE PRECISION;
  Ymax DOUBLE PRECISION;
  X DOUBLE PRECISION;
  Y DOUBLE PRECISION;
  sectors public.geometry[];
  i INTEGER;
BEGIN
  BoundM := ST_Transform($1, $3); --From WGS84 (SRID 4326) to the metric projection, to operate with step in meters
  Xmin := ST_XMin(BoundM);
  Xmax := ST_XMax(BoundM);
  Ymax := ST_YMax(BoundM);

  Y := ST_YMin(BoundM); --current sector's corner coordinate
  i := -1;
  <<yloop>>
  LOOP
    IF (Y > Ymax) THEN  --Better if generating polygons exceeds the bound for one step. You always can crop the result. But if not you may get not quite correct data for outbound polygons (e.g. if you calculate frequency per sector)
        EXIT;
    END IF;

    X := Xmin;
    <<xloop>>
    LOOP
      IF (X > Xmax) THEN
          EXIT;
      END IF;

      i := i + 1;
      sectors[i] := ST_GeomFromText('POLYGON(('||X||' '||Y||', '||(X+$2)||' '||Y||', '||(X+$2)||' '||(Y+$2)||', '||X||' '||(Y+$2)||', '||X||' '||Y||'))', $3);

      X := X + $2;
    END LOOP xloop;
    Y := Y + $2;
  END LOOP yloop;

  RETURN ST_Transform(ST_Collect(sectors), ST_SRID($1));
END;
$body$
LANGUAGE 'plpgsql';
")
```

#### Using the PL/SQL function to create the polygon grid

```{r}
if(RPostgres::dbExistsTable(pp_bst, DBI::Id(schema="tmp",table="spatevent")))
   {RPostgres::dbRemoveTable(pp_bst,DBI::Id(schema="tmp",table="spatevent"))}
RPostgres::dbExecute(pp_bst,
"CREATE TABLE tmp.spatevent AS(
WITH a AS(
    SELECT plot,min(ST_X(geometry)) min_x,min(ST_Y(geometry)) min_y,max(ST_X(geometry)) max_x,max(ST_Y(geometry)) max_y
    FROM tmp.parcelas
    GROUP BY plot 
), b AS(
SELECT plot,ST_SetSRID(ST_makePolygon(ST_MakeLine(ARRAY[st_makepoint(min_x,min_y),ST_MakePoint(min_x,max_y), ST_MakePoint(max_x,max_y), ST_MakePoint(max_x,min_y), ST_MakePoint(min_x,min_y)])),3116) geom
FROM a
), c AS(
SELECT plot, (ST_dump(public.makegrid_2d(ST_Transform(geom,3116),10,3116))).*
FROM b
), d AS(
SELECT plot, path, ROUND(ST_X(ST_Centroid(geom))) x_round, ROUND(ST_Y(ST_CENTROID(geom))) y_round
FROM c
), e AS(
SELECT x_round, RANK() OVER (PARTITION BY plot ORDER BY x_round) rank_x
FROM d
GROUP BY plot,x_round
), f AS(
SELECT DISTINCT ON (y_round) y_round, RANK() OVER (PARTITION BY plot ORDER BY y_round) rank_y
FROM d
GROUP BY plot, y_round
)
SELECT d.plot, path, rank_x, rank_y,ST_Transform(geom,3116) geom
FROM d
LEFT JOIN e USING (x_round)
LEFT JOIN f USING (y_round)
LEFT JOIN c USING (plot,path)
ORDER BY plot, path
)")
```

```{r}
max_x<-10
max_y<-10
RPostgres::dbExecute(pp_bst,
paste0("DELETE FROM tmp.spatevent
WHERE rank_x > ",max_x," OR rank_y > ",max_y))
```

##### subplot

```{r}
orderedSubplot<-data.frame(
  rank_x = rep(1:max_x,max_y),
  rank_y = rep(1:max_y,each=max_x),
  subplot = NA
)
counter<-0
for(i in seq(1,max_x,by=2))
{
  for(j in 1:max_y)
  {
    counter<-counter+1
    orderedSubplot$subplot[orderedSubplot$rank_x==i & orderedSubplot$rank_y==j]<-counter
  }
  i<-i+1
  for(j in max_y:1)
  {
    counter<-counter+1
    orderedSubplot$subplot[orderedSubplot$rank_x==i & orderedSubplot$rank_y==j]<-counter
  }
}
RPostgres::dbWriteTable(conn = pp_bst, name = DBI::Id(schema="tmp",table="subplotorder"), value = orderedSubplot, overwrite=T)
RPostgres::dbExecute(pp_bst, "ALTER TABLE tmp.spatevent ADD COLUMN IF NOT EXISTS subplot int")
```

```{r}
RPostgres::dbExecute(pp_bst, "UPDATE tmp.spatevent se SET subplot=spo.subplot FROM tmp.subplotorder spo WHERE se.rank_x=spo.rank_x AND se.rank_y=spo.rank_y")
```


```{r}
comp<-RPostgres::dbGetQuery(pp_bst,"
SELECT p.subplot pt, se.subplot spat
FROM tmp.parcelas p
LEFT JOIN tmp.spatevent se ON ST_Intersects(p.geometry,se.geom)
WHERE p.plot='LaPaz'")
sum(comp$pt==comp$spat)/nrow(comp)
comp<-RPostgres::dbGetQuery(pp_bst,"
SELECT p.subplot pt, se.subplot spat
FROM tmp.parcelas p
LEFT JOIN tmp.spatevent se ON ST_Intersects(p.geometry,se.geom)
WHERE p.plot='Matitas'")
sum(comp$pt==comp$spat,na.rm = T)/nrow(comp)
comp<-RPostgres::dbGetQuery(pp_bst,"
SELECT p.subplot pt, se.subplot spat
FROM tmp.parcelas p
LEFT JOIN tmp.spatevent se ON ST_Intersects(p.geometry,se.geom)
WHERE p.plot='Plato'")
sum(comp$pt==comp$spat)/nrow(comp)
```


### Inserting locations

#### Projects

```{r}
for(i in 1:4)
{
RPostgres::dbExecute(pp_bst, "DELETE FROM main.location WHERE cd_loc IN (
                     SELECT COALESCE(d.cd_loc,c.cd_loc,b.cd_loc,a.cd_loc)
                     FROM tmp.spatproject sp
                     LEFT JOIN main.location a ON sp.plot=a.location
                     LEFT JOIN main.location b ON b.parent_loc=a.cd_loc
                     LEFT JOIN main.location c ON c.parent_loc=b.cd_loc
                     LEFT JOIN main.location d ON d.parent_loc=c.cd_loc
                     WHERE (a.location IN (SELECT plot FROM tmp.spatproject)
                     OR b.location IN (SELECT plot FROM tmp.spatproject)
                     OR c.location IN (SELECT plot FROM tmp.spatproject)
                     OR d.location IN (SELECT plot FROM tmp.spatproject)
                     )
)")
}
RPostgres::dbExecute(pp_bst,
          "INSERT INTO main.location(location,cd_loc_type,cd_org_lev,pol_geom)
          SELECT plot, cd_loc_type, cd_org_lev, ST_Transform(geom, (SELECT srid FROM geometry_columns WHERE f_geometry_column = 'pol_geom' AND f_table_name = 'location'))
          FROM tmp.spatproject
          CROSS JOIN (SELECT cd_loc_type FROM main.def_location_type WHERE location_type='Plot polygon') a
          CROSS JOIN (SELECT cd_org_lev FROM main.def_organisation_level WHERE org_lev='project') b
          ")
```


#### Events

```{r}
RPostgres::dbExecute(pp_bst,
"INSERT INTO main.location(location, cd_loc_type, parent_loc, cd_org_lev, pol_geom)
SELECT plot || ': subplot ' || subplot, a.cd_loc_type,l.cd_loc parent_loc, b.cd_org_lev, ST_Transform(se.geom, (SELECT srid FROM geometry_columns WHERE f_geometry_column = 'pol_geom' AND f_table_name = 'location'))
FROM tmp.spatevent se
LEFT JOIN main.location l ON se.plot=l.location
CROSS JOIN (SELECT cd_loc_type FROM main.def_location_type WHERE location_type='Plot polygon') a
CROSS JOIN (SELECT cd_org_lev FROM main.def_organisation_level WHERE org_lev='event') b
ORDER BY l.cd_loc,subplot
")
```


```{r}
RPostgres::dbExecute(pp_bst,"DELETE FROM main.project WHERE project IN (SELECT plot FROM tmp.spatproject)")
RPostgres::dbExecute(pp_bst,
          "INSERT INTO main.project(project, project_description,cd_proj_type,cd_method,cd_loc)
          SELECT plot,NULL,cd_proj_type,cd_method,cd_loc
          FROM tmp.spatproject sm
          CROSS JOIN (SELECT cd_proj_type FROM main.def_project_type WHERE proj_type='permanent plot') a
          CROSS JOIN (SELECT cd_method FROM main.def_method WHERE method='Permanent plot 1 (to be defined)') b
          LEFT JOIN main.location ON sm.plot=location
          ")
```


## Inserting gp_events

```{r}
parcelas_tot$measuring_date <- as.Date(parcelas_tot$measuring_date, format="%d/%m/%y")
RPostgres::dbWriteTable(conn = pp_bst, name = DBI::Id(schema="tmp",table="completeplots"), value = parcelas_tot, overwrite = T)
(tab_gp_event<-RPostgres::dbGetQuery(conn=pp_bst, 
"WITH a AS(
SELECT DISTINCT cd_project, cd_loc, 'arbo' cd_gp_biol, a.cd_method, measuring_date date_begin, measuring_date date_end
FROM tmp.completeplots cp
LEFT JOIN main.project p ON p.project=cp.plot
CROSS JOIN (SELECT cd_method, method FROM main.def_method WHERE method='pp1_census0') a
)
SELECT a.*, ROW_NUMBER() OVER (PARTITION BY cd_project ORDER BY date_begin) AS compaign_nb
FROM a
"))
```


```{r}
stopifnot(table(tab_gp_event$cd_project)==1)
RPostgres::dbExecute(pp_bst,
"INSERT INTO main.gp_event(cd_project, cd_loc, cd_gp_biol, cd_method, date_begin, date_end, campaign_nb)
WITH a AS(
SELECT DISTINCT cd_project, cd_loc, 'arbo' cd_gp_biol, a.cd_method, measuring_date date_begin, measuring_date date_end
FROM tmp.completeplots cp
LEFT JOIN main.project p ON p.project=cp.plot
CROSS JOIN (SELECT cd_method, method FROM main.def_method WHERE method='pp1_census0') a
)
SELECT a.*, ROW_NUMBER() OVER (PARTITION BY cd_project ORDER BY date_begin) AS compaign_nb
FROM a
")
```


## Inserting events

```{r}
RPostgres::dbExecute(pp_bst, 
"WITH a AS(
  SELECT p.project, cd_gp_event, date_begin date_gp_event
  FROM main.gp_event ge
  LEFT JOIN main.project p USING (cd_project)
  WHERE p.project IN (SELECT plot FROM tmp.completeplots)
)
INSERT INTO main.event(event_id, cd_gp_event, num_replicate, description_replicate, date_begin, date_end, cd_loc)
SELECT project||'_census0_subplot'||subplot, cd_gp_event, subplot, 'subplot '||subplot||'/100', date_gp_event, date_gp_event, cd_loc
FROM a
CROSS JOIN (SELECT generate_series(1,100) subplot) b 
LEFT JOIN main.location ON location=a.project||': subplot '||b.subplot
ORDER BY cd_gp_event, subplot
")
```


```{r}
events<-RPostgres::dbReadTable(pp_bst,DBI::Id(schema="main",table="event"))
m<-match(paste0(parcelas_tot$plot,"_census0_subplot",trimws(parcelas_tot$subplot)),events$event_id)
parcelas_tot$cd_event<-events$cd_event[m]
```

### Correction to the falsely attribruted subplots

```{r}
sf_event <- st_read(pp_bst,query="
SELECT e.*,pol_geom
FROM main.project
LEFT JOIN main.gp_event ge USING (cd_project)
LEFT JOIN main.event e USING (cd_gp_event)
LEFT JOIN main.location l ON e.cd_loc=l.cd_loc
WHERE project IN ('LaPaz','Matitas','Plato')
")
sjpe <- st_join(sf_parcelas,sf_event)

# Plato subparcelas 14 -> 13
idToChange<-sjpe$id[sjpe$plot=="Plato" & sjpe$subplot==14 & sjpe$num_replicate==13]
newEvent <- RPostgres::dbGetQuery(pp_bst,"SELECT cd_event FROM main.event LEFT JOIN main.gp_event USING (cd_gp_event) LEFT JOIN main.project USING (cd_project) WHERE project='Plato' AND num_replicate=13")$cd_event
parcelas_tot[parcelas_tot$id %in% idToChange,"subplot"]<-13
parcelas_tot[parcelas_tot$id %in% idToChange,"cd_event"]<-newEvent

# Plato subparcelas 45 -> 44
idToChange<-sjpe$id[sjpe$plot=="Plato" & sjpe$subplot==45 & sjpe$num_replicate==44]
newEvent <- RPostgres::dbGetQuery(pp_bst,"SELECT cd_event FROM main.event LEFT JOIN main.gp_event USING (cd_gp_event) LEFT JOIN main.project USING (cd_project) WHERE project='Plato' AND num_replicate=44")$cd_event
parcelas_tot[parcelas_tot$id %in% idToChange,"subplot"]<-44
parcelas_tot[parcelas_tot$id %in% idToChange,"cd_event"]<-newEvent

```




## Inserting projects

## Taxonomy

### Getting suggestions and validation from rdsTaxVal

```{r}
library(rdsTaxVal)
taxo_parcelas<-new_taxo_oneTab(obj=parcelas_tot,currentFormat = "oneTable", taxonRanks_names = c(family="family",genus="genus",species="specificEpithet"), taxonRanks_epithetized = "specificEpithet",taxoCode = NA, comments = "comments",plot = "plot")
suggested_parcelas<-fullTaxonomicDiagnostic(taxo_parcelas,argsCheckFunction = list())
corrected_parcelas<-correct(taxo_parcelas,suggested_parcelas)
```

```{r}
suggestTAB<-suggested_parcelas$suggested
```

Comparing with the TDF reference (the idea is that has already been reviewed in other validation run from other datasets)

```{r}
load("../../otherData/TDF_taxonomicReference.RData")
notInTdfRef<-which(!getLowerTax(corrected_parcelas) %in% tdfTaxa$canonicalname)
correctNotInTdfRef<-intersect(suggestTAB$row,notInTdfRef)
```

Los casos que corresponden a correcciones automáticas,que no resultan en taxones que ya se validaron en TDF y que no son simplemente "misplaced qualifiers":
```{r}
kableExtra::kable(unique(suggestTAB[suggestTAB$row%in%correctNotInTdfRef & !suggestTAB$suggestDescription=="misplaced qualifiers for undetermined taxa",c("suggestDescription","family","genus","specificEpithet","suggest_family","suggest_genus","suggest_specificEpithet","suggest_verbatimTaxonRank")]))
```

```{r}
completeClassifparcelas<-extractCompleteTaxo(suggested_parcelas$analysedGbif,addLocalId = T,addAvailableAuthorship = T, getUnavailableAuthorship = T, getSynonyms = T)
finalTaxParcelas<-getLowerTax(corrected_parcelas)
casesToAdd<-extract(corrected_parcelas,"taxonRanks")[!is.na(finalTaxParcelas) &!finalTaxParcelas %in% completeClassifparcelas$canonicalname,]
stopifnot(nrow(casesToAdd)==0)
completeClassifparcelas$parent_localId <- completeClassifparcelas$localId[match(completeClassifparcelas$parent_gbifid , completeClassifparcelas$gbifid)]
```


### Sending taxonomy to the database

```{r}
library(RPostgres)
pp_bst<-dbConnect(Postgres(),dbname="pp_bst_col")
dbExecute(pp_bst,"UPDATE main.taxo SET cd_accepted=cd_tax WHERE cd_accepted IS NULL")
intoDB<-addClassifToDb(completeClassifparcelas, pp_bst)
corrected_parcelas$tax_localId <- completeClassifparcelas$localId [ match(finalTaxParcelas, completeClassifparcelas$canonicalname) ]
correctedParcelas<-addIdentifier(corrected_parcelas,"tax_localId",nameID = "Local taxon ID", typeID = "local", nameSource = "local R Session")
corrected_parcelas$cd_tax <- intoDB$final_cd_tax[match(corrected_parcelas$tax_localId, intoDB$localId)]
corrected_parcelas<-addIdentifier(corrected_parcelas,"cd_tax",nameID = "Database taxon ID", typeID="database", nameSource="pp_bst_col")
```


### Working on morpho-taxonomy

```{r}
mTax<-getMorphoTaxo(corrected_parcelas)
w_mTax<-which(!is.na(mTax))
mTax<-mTax[w_mTax]
```

Morphotaxa need to be defined either for a project, a group of event or an event, here we will use the projects, which correspond to the plots.

```{r}
un_plots<-unique(corrected_parcelas$plot)
un_cd_projects<-unlist(sapply(paste0("SELECT cd_project FROM main.project WHERE project=",RPostgres::dbQuoteString(pp_bst,plots)),RPostgres::dbGetQuery, conn=pp_bst, USE.NAMES = F),use.names = F)
cd_projects<-un_cd_projects[match(corrected_parcelas$plot,un_plots)]
```

Morpho taxa must be defined with a type.
```{r}
getMorphoType<-function(taxo)
{
  stopifnot(methods::is(taxo,"taxo_oneTab"))
  ATTR_mq <- attributes(taxo)$morphoQualifiers
  mqTab <- extract(taxo, "morphoQualifiers")
  nbQualifiers<-apply(mqTab, 1, function(x) sum(!is.na(x)))
  if(any(nbQualifiers>1))
  {stop("Some taxa have more than one qualifier (see extract(taxo, \"morphoQualifiers\")")}
  MT  <- rep(NA_character_, nrow(taxo) )
  if("sp_specif" %in% names(ATTR_mq))
  {
    colSp_specif<-ATTR_mq["sp_specif"]
    MT[grep("^spp?\\.? *$",taxo[,colSp_specif])]<-"Unspecified species"
    MT[grep("^[Ss]p ?\\.?[0-9]+",taxo[,colSp_specif])]<-"Numbered undetermined species"
    if(any(!is.na(taxo[,colSp_specif]) & is.na(MT))) {warning("Undertermined morpho-taxa types")}
  }
  if("cf_aff" %in% names(ATTR_mq))
  {
    colCf_aff<-ATTR_mq["cf_aff"]
    MT[!is.na(taxo[colCf_aff])]<-"Confere or affinity"
  }
  return(MT)
}
table(getMorphoType(corrected_parcelas))
```


```{r}
dbExecute(pp_bst,paste0("DELETE FROM main.morfo_taxo WHERE def_for_project IN (",paste(un_cd_projects,collapse=","),")"))
morphoToSend<-unique(data.frame(cd_tax=corrected_parcelas$cd_tax,
           morphotaxon_type=getMorphoType(corrected_parcelas),
           name_morfo=getMorphoTaxo(corrected_parcelas),
           pseudo_rank=ifelse(grepl("species",getMorphoType(corrected_parcelas)),"SP",NA),
           verbatim_taxon_rank=corrected_parcelas$verbatimTaxonRank,
           def_for_project=cd_projects
           )[w_mTax,])
dbAppendTable(pp_bst,Id(schema="main",table="morfo_taxo"),morphoToSend)
dbMT<-dbReadTable(pp_bst,Id(schema="main",table="morfo_taxo"))
dbToMatch<-as.matrix(dbMT[c("name_morfo","def_for_project")])
localMT<-as.matrix(data.frame(name_morfo=getMorphoTaxo(corrected_parcelas), def_for_project=cd_projects))
corrected_parcelas$cd_morfo<-dbMT$cd_morfo[match(split(localMT,row(localMT)),split(dbToMatch,row(dbToMatch)))]
#addIdentifier(corrected_parcelas,"cd_morfo",nameID = "Database Morphotaxon ID", typeID="Database",nameSource = "pp_bst_col")
```

### Determination




Determinations make sense at the individual case.
Here are the correspondance between rows and individuals:

```{r}
stopifnot(is.character(corrected_parcelas$ind))
matInd<-as.matrix(corrected_parcelas[c("plot","subplot","ind")])
ind_idx<-match(split(matInd,row(matInd)),split(matInd,row(matInd)))
tax_ind<-by(corrected_parcelas,ind_idx,function(tab)unique(tab[c("cd_tax","cd_morfo")]))
un_taxInd<-sapply(tax_ind,nrow)==1
sum(!un_taxInd)
pb_ind<-as.numeric(names(un_taxInd)[!un_taxInd])
write.csv(x = corrected_parcelas[ind_idx %in% pb_ind,c("plot","subplot","ind","cd_tax","cd_morfo","genus","specificEpithet","verbatimTaxonRank")], file = "../../problemIndividualTaxo.csv")
```


```{r}
solution<-read.csv("../../problemIndividualTaxo_soluciónNatalia.csv",sep=";", encoding = "latin1")
```

I've got a problem here: each time I apply the code from this document, the cd_morfo variable is deleted and created another time, which means that with the serial type, it increment the minimal values as the last max value +1. So it does not correspond.


The only solution is to test whether the tables have the same order and to replace
```{r}
stopifnot(solution$cd_tax==corrected_parcelas$cd_tax[ind_idx %in% pb_ind])
stopifnot(solution$ind==corrected_parcelas$ind[ind_idx %in% pb_ind])

```

```{r}
solution$cd_morfo<-corrected_parcelas$cd_morfo[ind_idx %in% pb_ind]
```



```{r}
#solution$tagToChange<- gsub("[A-z ]*([0-9]+\\.?[0-9]?[A-Z]?)$","\\1",solution$correccion)
matCorrec<-as.matrix(solution[c("plot","subplot","ind","cd_tax","cd_morfo")])
matCorrec[grep("^ +",matCorrec)]<-gsub("^ +","",matCorrec[grep("^ +",matCorrec)])
matParcelas<-as.matrix(corrected_parcelas[c("plot","subplot","ind","cd_tax","cd_morfo")])
matParcelas[grep("^ +",matParcelas)]<-gsub("^ +","",matParcelas[grep("^ +",matParcelas)])
m<-match(split(matCorrec,row(matCorrec)),split(matParcelas,row(matParcelas)))
#m<-match(split(matParcelas,row(matParcelas)),split(matCorrec,row(matCorrec)))
pbToResolve<-unique(ind_idx[m])
ind_idx_v2<-ind_idx
min_new_idx<-nrow(corrected_parcelas) + 1
for(i in 1:length(pbToResolve))
{
  c_idx <-pbToResolve[i]
  s <- solution[ind_idx[m]==c_idx,]
  p <- corrected_parcelas[ind_idx==c_idx,]
  stopifnot(nrow(s)==nrow(p))
  mt <- as.matrix(p[c("cd_tax", "cd_morfo")])
  m_mt <- match(split(mt,row(mt)),split(mt,row(mt)))
  changeInd <- s$correccion != ""
  if(sum(changeInd) > 0)
  {
    stopifnot(sum(changeInd)==1) # If there is cases where more than one file should change individualID, the code should be more complex, understand if there are more than one row corresponding to the same individual etc.
    c_plot <- s$plot[1]
    c_subplot <- s$subplot[1]
    c_ind <- s$ind[1]
    potentialInd <- paste(c_ind,1:50,sep=".")
    alreadyInd<-corrected_parcelas$ind[corrected_parcelas$plot == c_plot & corrected_parcelas$subplot == c_subplot]
    newInd<-potentialInd[!potentialInd%in%alreadyInd][1]
    corrected_parcelas$ind[ind_idx==c_idx][changeInd]<-newInd
    corrected_parcelas$individualID[ind_idx==c_idx][changeInd]<-newInd
    corrected_parcelas$ramet[ind_idx==c_idx][changeInd]<-1
    ind_idx_v2[ind_idx==c_idx][changeInd]<-max(min_new_idx,max(ind_idx_v2)+1)
    newIdxs<-ind_idx_v2[ind_idx==c_idx]
    resolved<-all(tapply(newIdxs,m_mt,function(x)length(unique(x)))==1)
  }
  if(sum(changeInd) == 0 || (sum(changeInd)>0 & !resolved))
  {
    stopifnot(tapply(s$selecci.n,m_mt,function(x)length(unique(x)))==1)
    corr_family<-p$family[s$selecci.n==1][1]
    corr_genus<-p$genus[s$selecci.n==1][1]
    corr_specificEpithet<-p$specificEpithet[s$selecci.n==1][1]
    corr_authorName<-p$authorName[s$selecci.n==1][1]
    corr_cd_tax<-p$cd_tax[s$selecci.n==1][1]
    corr_cd_morfo<-p$cd_tax[s$selecci.n==1][1]
    corr_tax_localId<-p$tax_localId[s$selecci.n==1][1]
    corr_verbatimTaxonRank<-p$verbatimTaxonRank[s$selecci.n==1][1]
    corrected_parcelas$family[ind_idx==c_idx][s$selecci.n==0]<-corr_family
    corrected_parcelas$genus[ind_idx==c_idx][s$selecci.n==0]<-corr_genus
    corrected_parcelas$specificEpithet[ind_idx==c_idx][s$selecci.n==0]<-corr_specificEpithet
    corrected_parcelas$authorName[ind_idx==c_idx][s$selecci.n==0]<-corr_authorName
    corrected_parcelas$cd_tax[ind_idx==c_idx][s$selecci.n==0]<-corr_cd_tax
    corrected_parcelas$cd_morpho[ind_idx==c_idx][s$selecci.n==0]<-corr_cd_morfo
    corrected_parcelas$tax_localId[ind_idx==c_idx][s$selecci.n==0]<-corr_tax_localId
    corrected_parcelas$verbatimTaxonRank[ind_idx==c_idx][s$selecci.n==0]<-corr_verbatimTaxonRank
  }
}
```


There is a problem for various individuals which have more than one taxon depending on the ramet.
```{r}
majority<-function(mat)
{
  m<-match(split(mat,row(mat)),split(mat,row(mat)))
  return(as.numeric(names(sort(table(m),decreasing = T))[1]))
}
all(sapply(tax_ind,function(x)majority(as.matrix(x)))==1)
```

## Inserting determination, register, individual and coordinates




```{r}
corrected_parcelas$recordNumber[corrected_parcelas$recordNumber==""]<-NA
matInd<-as.matrix(corrected_parcelas[c("plot","subplot","ind")])
ind_idx<-match(split(matInd,row(matInd)),split(matInd,row(matInd)))
ind_tab<-corrected_parcelas[unique(ind_idx),]
ind_tab$cd_project<-cd_projects[unique(ind_idx)]
ind_tab$cd_identif<-NA
ind_tab$cd_reg<-NA
ind_tab$cd_ind<-NA
dateIdentif<-as.Date("1/10/2025",format="%d/%m/%Y")
stopifnot(sum(!is.na(ind_tab$recordNumber)) == sum(!is.na(corrected_parcelas$recordNumber)))
dbBegin(pp_bst)
for(i in 1:nrow(ind_tab))
{
  cd_reg<-RPostgres::dbGetQuery(pp_bst,paste0("INSERT INTO main.register(cd_event, date_reg, qt_int)
         VALUES(",
         dbQuoteLiteral(pp_bst,ind_tab$cd_event[i]),",",
         dbQuoteLiteral(pp_bst,ind_tab$measuring_date[i]),",",
         1,")
         RETURNING cd_reg")
         )$cd_reg
  cd_identif <- RPostgres::dbGetQuery(pp_bst,paste0("INSERT INTO main.identification (cd_reg,cd_tax, cd_morfo, date_identif, catalog_id) VALUES(",
         dbQuoteLiteral(pp_bst,cd_reg),",",
         dbQuoteLiteral(pp_bst,ind_tab$cd_tax[i]),",",
         dbQuoteLiteral(pp_bst,ind_tab$cd_morfo[i]),",",
         dbQuoteLiteral(pp_bst,dateIdentif),",",
         dbQuoteLiteral(pp_bst,ind_tab$recordNumber[i]),
         ")
         RETURNING cd_identif")
  )$cd_identif
  if(!is.na(ind_tab$latitude_decimal[i])&!is.na(ind_tab$longitude_decimal[i]))
  {
    RPostgres::dbExecute(pp_bst,
    paste0("INSERT INTO main.register_location
           VALUES(",
           dbQuoteLiteral(pp_bst,cd_reg),",",
           "ST_Transform(ST_SetSRID(",
           "ST_MakePoint(",dbQuoteLiteral(pp_bst,ind_tab$longitude_decimal[i]),",",dbQuoteLiteral(pp_bst,ind_tab$latitude_decimal[i]),"),",dbQuoteLiteral(pp_bst,as.integer(CRS_orig)),"),",dbQuoteLiteral(pp_bst,as.integer(CRS)),"))"
           ))
  }
   cd_ind<-RPostgres::dbGetQuery(pp_bst,paste0("INSERT INTO main.individual(tag,uniq_in_project) VALUES(
         ", dbQuoteLiteral(pp_bst,ind_tab$ind[i]),",",# NOTE THIS WILL NOT ALWAYS WORK, WE MAY HAVE TO EXTRACT THE individual code from the tag
         dbQuoteLiteral(pp_bst,ind_tab$cd_project[i]),
         ") RETURNING cd_ind" 
         ))$cd_ind
  RPostgres::dbExecute(pp_bst,paste0("INSERT INTO main.reg_individual VALUES(",dbQuoteLiteral(pp_bst,cd_ind),",",dbQuoteLiteral(pp_bst,cd_reg),")"))
  ind_tab$cd_identif[i]<-cd_identif
  ind_tab$cd_reg[i]<-cd_reg
  ind_tab$cd_ind[i]<-cd_ind
}
dbCommit(pp_bst)
m<-match(ind_idx,unique(ind_idx))
corrected_parcelas$cd_identif<-ind_tab$cd_identif[m]
corrected_parcelas$cd_reg<-ind_tab$cd_reg[m]
corrected_parcelas$cd_ind<-ind_tab$cd_ind[m]

```

## Inserting subindividual


Inserting the ramet subpart:

```{r}
subind_part <- RPostgres::dbReadTable(pp_bst,DBI::Id(schema="main",table="def_subindividual_part"))
if("ramet" %in% subind_part$part)
{
  cd_part <- subind_part$cd_part[subind_part$part=="ramet"]
} else {
  RPostgres::dbAppendTable(pp_bst, DBI::Id(schema="main",table="def_subindividual_part"),
                           data.frame(
                             part = "ramet",
                             cd_gp_biol ="arbo"
                           ))
  subind_part <- RPostgres::dbReadTable(pp_bst,DBI::Id(schema="main",table="def_subindividual_part"))
  cd_part <- subind_part$cd_part[subind_part$part=="ramet"]
}
```

Inserting the variables

```{r}
vars<-RPostgres::dbGetQuery(pp_bst, "SELECT cd_var,name_var,org_lev FROM main.def_var dv LEFT JOIN main.def_organisation_level USING (cd_org_lev);")
if(any(vars$name_var=="dbh_cm" & vars$org_lev=="sub-individual characteristics"))
{
  cd_var_dbh_cm <- vars$cd_var[vars$name_var=="dbh_cm" & vars$org_lev=="sub-individual characteristics"]
} else{
  units<-RPostgres::dbGetQuery(pp_bst,"SELECT cd_unit, unit, measurement_type FROM main.def_unit LEFT JOIN main.def_measurement_type USING (cd_measurement_type)")
  if(any(units$unit=="centimeter" & units$measurement_type=="length"))
  {cd_unit_cm<-units$cd_unit[units$unit=="centimeter" & units$measurement_type=="length"]
  }else{
    cd_unit_cm<-dbGetQuery(pp_bst,paste0("INSERT INTO main.def_unit(cd_measurement_type,unit,unit_spa,abbv_unit,factor)
VALUES((SELECT cd_measurement_type FROM main.def_measurement_type WHERE measurement_type = 'length')",",",
RPostgres::dbQuoteLiteral(pp_bst,"centimeter"),",",
RPostgres::dbQuoteLiteral(pp_bst,"centímetro"),",",
RPostgres::dbQuoteLiteral(pp_bst,"cm"),",",
RPostgres::dbQuoteLiteral(pp_bst,0.001),
") RETURNING cd_unit"))$cd_unit
  }
  cd_var_dbh_cm<-dbGetQuery(pp_bst,paste0("INSERT INTO main.def_var(cd_unit,cd_org_lev,name_var,description,extra_var,extension_dwc,type_var,repeatable) VALUES(",
RPostgres::dbQuoteLiteral(pp_bst,cd_unit_cm),",
(SELECT cd_org_lev FROM main.def_organisation_level WHERE org_lev='sub-individual characteristics'),",
RPostgres::dbQuoteLiteral(pp_bst,"dbh_cm"),",",
RPostgres::dbQuoteLiteral(pp_bst,"Diameter at breast height"),",",
RPostgres::dbQuoteLiteral(pp_bst,T),",",
RPostgres::dbQuoteLiteral(pp_bst,'MeasurementOrFact'),",",
RPostgres::dbQuoteLiteral(pp_bst,"double precision"),",",
RPostgres::dbQuoteLiteral(pp_bst,F),")
RETURNING cd_var"
    ))$cd_var
}

if(any(vars$name_var=="height_m" & vars$org_lev=="sub-individual characteristics"))
{
  cd_var_height_m <- vars$cd_var[vars$name_var=="height_m" & vars$org_lev=="sub-individual characteristics"]
} else{
  units<-RPostgres::dbGetQuery(pp_bst,"SELECT cd_unit, unit, measurement_type FROM main.def_unit LEFT JOIN main.def_measurement_type USING (cd_measurement_type)")
  if(any(units$unit=="meter" & units$measurement_type=="length"))
  {cd_unit_m<-units$cd_unit[units$unit=="meter" & units$measurement_type=="length"]
  }else{
    cd_unit_m<-dbGetQuery(pp_bst,paste0("INSERT INTO main.def_unit(cd_measurement_type,unit,unit_spa,abbv_unit,factor)
VALUES((SELECT cd_measurement_type FROM main.def_measurement_type WHERE measurement_type = 'length')",",",
RPostgres::dbQuoteLiteral(pp_bst,"meter"),",",
RPostgres::dbQuoteLiteral(pp_bst,"metro"),",",
RPostgres::dbQuoteLiteral(pp_bst,"m"),",",
RPostgres::dbQuoteLiteral(pp_bst,1),
") RETURNING cd_unit"))$cd_unit
  }
  cd_var_height_m<-dbGetQuery(pp_bst,paste0("INSERT INTO main.def_var(cd_unit,cd_org_lev,name_var,description,extra_var,extension_dwc,type_var,repeatable) VALUES(",
RPostgres::dbQuoteLiteral(pp_bst,cd_unit_m),",
(SELECT cd_org_lev FROM main.def_organisation_level WHERE org_lev='sub-individual characteristics'),",
RPostgres::dbQuoteLiteral(pp_bst,"height_m"),",",
RPostgres::dbQuoteLiteral(pp_bst,"Height of a ramet"),",",
RPostgres::dbQuoteLiteral(pp_bst,T),",",
RPostgres::dbQuoteLiteral(pp_bst,'MeasurementOrFact'),",",
RPostgres::dbQuoteLiteral(pp_bst,"double precision"),",",
RPostgres::dbQuoteLiteral(pp_bst,F),")
RETURNING cd_var"
    ))$cd_var
}
```




```{r}
corrected_parcelas$cd_project<-cd_projects
### TODO: manage that!
corrected_parcelas[7954,"ramet"]<-6
mat_ramet<-as.matrix(corrected_parcelas[c("plot","subplot","ind","ramet")])
pbRamets<-which(!match(split(mat_ramet,row(mat_ramet)),split(mat_ramet,row(mat_ramet)))==1:nrow(mat_ramet))
if(length(pbRamets)>0)
 {corrected_parcelas<-corrected_parcelas[-pbRamets,]}
####

mat_ramet<-as.matrix(corrected_parcelas[c("plot","subplot","ind","ramet")])
stopifnot(match(split(mat_ramet,row(mat_ramet)),split(mat_ramet,row(mat_ramet)))==1:nrow(mat_ramet))

corrected_parcelas$cd_subind<-NA
dbBegin(pp_bst)
for(i in 1:nrow(corrected_parcelas))
{
  cd_subind<-RPostgres::dbGetQuery(pp_bst,paste0(
    "INSERT INTO main.subindividual(cd_ind,cd_part,part_number,uniq_in_project,tag) VALUES(",
    RPostgres::dbQuoteLiteral(pp_bst,corrected_parcelas$cd_ind[i]),",",
    RPostgres::dbQuoteLiteral(pp_bst,cd_part),",",
    RPostgres::dbQuoteLiteral(pp_bst,corrected_parcelas$ramet[i]),",",
    RPostgres::dbQuoteLiteral(pp_bst,corrected_parcelas$cd_project[i]),",",
    RPostgres::dbQuoteLiteral(pp_bst,corrected_parcelas$individualID[i]),"
    ) RETURNING cd_subind"
  ))$cd_subind
  if(!is.na(corrected_parcelas$DBH_cm[i])){
  RPostgres::dbExecute(pp_bst,paste0(
    "INSERT INTO main.subindividual_characteristics(cd_reg,cd_subind,cd_var,subind_char_double)
    VALUES(",
    RPostgres::dbQuoteLiteral(pp_bst,corrected_parcelas$cd_reg[i]),",",
    RPostgres::dbQuoteLiteral(pp_bst,cd_subind),",",
    RPostgres::dbQuoteLiteral(pp_bst,cd_var_dbh_cm),",",
    RPostgres::dbQuoteLiteral(pp_bst,corrected_parcelas$DBH_cm[i]),
    ")"
  ))
  }
  if(!is.na(corrected_parcelas$height_m[i])){
  RPostgres::dbExecute(pp_bst,paste0(
    "INSERT INTO main.subindividual_characteristics(cd_reg,cd_subind,cd_var,subind_char_double)
    VALUES(",
    RPostgres::dbQuoteLiteral(pp_bst,corrected_parcelas$cd_reg[i]),",",
    RPostgres::dbQuoteLiteral(pp_bst,cd_subind),",",
    RPostgres::dbQuoteLiteral(pp_bst,cd_var_height_m),",",
    RPostgres::dbQuoteLiteral(pp_bst,corrected_parcelas$height_m[i]),
    ")"
  ))
  }
  corrected_parcelas$cd_subind[i] <- cd_subind
}
dbCommit(pp_bst)
```



## Creating the occurrenceID



```{sql}
#| connection = pp_bst
WITH a AS(
SELECT r.cd_reg,
  CASE
    WHEN COALESCE(voucher, catalog_id) IS NULL THEN 'ObservacionHumana'
    ELSE 'PreservedSpecimen'
    END basis_of_record
FROM main.register r
LEFT JOIN main.identification i USING (cd_reg)
)
SELECT cd_reg, project, 'IAvH:'||UPPER(basis_of_record)||':'||UPPER(project)||'_CENSUS0:'||LPAD( (ROW_NUMBER() OVER (PARTITION BY cd_project ORDER BY cd_project,cd_reg))::text,4,'0') occurrence_id
FROM main.register r
LEFT JOIN main.event e USING (cd_event)
LEFT JOIN main.gp_event ge USING (cd_gp_event)
LEFT JOIN main.project p USING (cd_project)
LEFT JOIN a USING(cd_reg)
WHERE project IN ('LaPaz','Matitas','Plato')

```
```{r}
reg_occurrenceId<-dbGetQuery(pp_bst,"
WITH b AS(
SELECT cd_reg, project, 'IAVH:'||'OBSERVACIONHUMANA'||':'||UPPER(project)||'_CENSUS0:'||LPAD( (ROW_NUMBER() OVER (PARTITION BY cd_project ORDER BY cd_project,cd_reg))::text,4,'0') occurrence_id
FROM main.register r
LEFT JOIN main.event e USING (cd_event)
LEFT JOIN main.gp_event ge USING (cd_gp_event)
LEFT JOIN main.project p USING (cd_project)
WHERE project IN ('LaPaz','Matitas','Plato')
)UPDATE main.register AS r
SET occurrence_id=b.occurrence_id
FROM b
WHERE b.cd_reg=r.cd_reg AND r.occurrence_id IS NULL
RETURNING r.cd_reg, r.occurrence_id")
stopifnot(all(is.na(corrected_parcelas$occurrenceID)))
corrected_parcelas$occurrenceID<-reg_occurrenceId$occurrence_id[match(corrected_parcelas$cd_reg,reg_occurrenceId$cd_reg)]
```


## Checking final quality

Most likely, the problems we will find here will be corrected in a previous part of the code, so the results here won't show them anymore, but it is helpful to keep the checks here!


```{sql}
#| connection=pp_bst
WITH a AS(
SELECT project,event_id,location, substring(event_id FROM '[0-9]+$') subplot_event, substring(location FROM '[0-9]+$') subplot_location
FROM main.register_location rl
LEFT JOIN main.register USING (cd_reg)
LEFT JOIN main.event USING (cd_event)
LEFT JOIN main.gp_event USING (cd_gp_event)
LEFT JOIN main.project USING (cd_project)
LEFT JOIN main.location l ON l.cd_org_lev=6 AND ST_intersects(rl.pt_geom,l.pol_geom) 
),b AS(
SELECT project,subplot_event,subplot_location,count(*)
FROM a
GROUP BY project,subplot_event,subplot_location
),c AS(
SELECT DISTINCT ON (project,subplot_event) project, subplot_event, subplot_location
FROM b
ORDER BY project,subplot_event,count DESC
)
SELECT *
FROM c
WHERE subplot_event<>subplot_location
```




```{r}
save(corrected_parcelas,file="../../inserted_3parcelas_backup.RData")
```


## Adding people

```{r}
people <- RPostgres::dbReadTable(pp_bst, DBI::Id(schema = "main", table = "people"))
if(!"Roy González-M" %in% people$preferred_complete)
{
  dbExecute(pp_bst,
"INSERT INTO main.people(
  verbatim_person,
  first_name1,
  first_name2,
  family_name1,
  family_name2,
  preferred_complete,
  preferred_first,
  preferred_family,
  gender,
  birth)
VALUES
  ('Roy González-M','Roy','Oswaldo', 'González', 'Martinez', 'Roy González-M', 'Roy', 'González-M', 'M', NULL),
  ('Álvaro Idárraga-Piedrahita', 'Álvaro', NULL, 'Idárraga',  'Piedrahita',  'Álvaro Idárraga-Piedrahita',  'Álvaro',  'Idárraga-Piedrahita',  'M', NULL),
  ('Marius Bottin',  'Marius',  'Jean',  'Bottin',  NULL,  'Marius Bottin'  ,'Marius',  'Bottin'  ,'M', DATE '1984-12-18'),
('Natalia Norden','Natalia',NULL,'Norden','Medina','Natalia Norden','Natalia','Norden','F',NULL)
")
}
orga<-RPostgres::dbReadTable(pp_bst,DBI::Id(schema="main",table="organization"))
if(!'IAvH' %in% orga$org_abbrev)
{
  RPostgres::dbExecute(pp_bst,"INSERT INTO main.organization(org_name, org_abbrev, cd_org_type)
VALUES('Instituto de Investigación de Recursos Biológicos Alexander von Humboldt','IAvH',(SELECT cd_org_type FROM main.organization_type WHERE org_type='public institution'))")
}
if(!'UT' %in% orga$org_abbrev)
{
  RPostgres::dbExecute(pp_bst,"INSERT INTO main.organization(org_name, org_abbrev, cd_org_type)
VALUES('Universidad del Tolima','UT',(SELECT cd_org_type FROM main.organization_type WHERE org_type='public institution'))")
}
if(!'JAUM' %in% orga$org_abbrev)
{
  RPostgres::dbExecute(pp_bst,"INSERT INTO main.organization(org_name, org_abbrev, cd_org_type)
VALUES('Jardín Botánico de Medellín Joaquín Antonio Uribe','JAUM',(SELECT cd_org_type FROM main.organization_type WHERE org_type='private institution'))")
}
```


```{r}
RPostgres::dbGetQuery(pp_bst,
"WITH a AS(
SELECT 
  (SELECT cd_person FROM main.people WHERE preferred_complete='Roy González-M') cd_person,
  (SELECT cd_org FROM main.organization WHERE org_abbrev='UT') cd_org,
  'Professor' AS role,
  DATE(NOW()) AS date_apply
UNION ALL
SELECT 
  (SELECT cd_person FROM main.people WHERE preferred_complete='Álvaro Idárraga-Piedrahita') cd_person,
  (SELECT cd_org FROM main.organization WHERE org_abbrev='JAUM') cd_org,
  'Director del herbario' AS role,
  DATE(NOW()) AS date_apply
)
INSERT INTO main.people_role(cd_person, cd_org, role, date_apply)
SELECT a.*
FROM a
LEFT JOIN main.people_role pr USING (cd_person,cd_org,role)
WHERE pr.cd_people_role IS NULL")
```

```{sql}
#| connection=pp_bst
WITH a AS(
SELECT ARRAY[cd_people_role] identified_by
FROM main.people_role
LEFT JOIN main.people USING(cd_person)
LEFT JOIN main.organization USING (cd_org)
WHERE preferred_complete='Álvaro Idárraga-Piedrahita' AND org_abbrev='JAUM'
), b AS(
SELECT cd_reg,identified_by
FROM main.register r
CROSS JOIN a
LEFT JOIN main.event e USING (cd_event)
LEFT JOIN main.gp_event USING (cd_gp_event)
LEFT JOIN main.project USING (cd_project)
WHERE project IN ('LaPaz','Matitas','Plato')
),c AS(
UPDATE main.identification i
SET identified_by=b.identified_by
FROM b
WHERE i.cd_reg=b.cd_reg
RETURNING i.cd_reg, i.identified_by
)
SELECT *
FROM c
LIMIT 10
```

```{sql}
#| connection=pp_bst
WITH a AS(
SELECT ARRAY[cd_people_role] cds_recorded_by
FROM main.people_role
LEFT JOIN main.people USING(cd_person)
LEFT JOIN main.organization USING (cd_org)
WHERE preferred_complete='Roy González-M' AND org_abbrev='UT'
), b AS(
SELECT cd_reg,a.cds_recorded_by
FROM main.register r
CROSS JOIN a
LEFT JOIN main.event e USING (cd_event)
LEFT JOIN main.gp_event USING (cd_gp_event)
LEFT JOIN main.project USING (cd_project)
WHERE project IN ('LaPaz','Matitas','Plato')
),c AS(
UPDATE main.register r
SET cds_recorded_by=b.cds_recorded_by
FROM b
WHERE r.cd_reg=b.cd_reg
RETURNING r.cd_reg, r.cds_recorded_by
)
SELECT *
FROM c
LIMIT 10
```


## Shutting down light...

```{r}
dbDisconnect(pp_bst)
```


